---
title: "Avocado_price"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Time Series ML
library(tidymodels)
library(modeltime)

# Core
library(tidyverse)
library(timetk)
library(lubridate)

# Import & clean
library(readr)
library(janitor)
library(DataExplorer)
```


```{r}
variables <- (.date_var=date,
            .value=average_price)
```


```{r Loading the data & DQ checks}
# A.Loading the data & DQ checks ----

# Load data
avocado_raw <- read_csv("00_Data/avocado.csv") %>% 
  clean_names() %>% 
  select(-1)

# Data retrieve from Kaggle : https://www.kaggle.com/neuromusic/avocado-prices


avocado_raw %>% glimpse()


# Checking Data quality 

avocado_raw %>% 
  DataExplorer::plot_missing()
```

Data has no missing value

## Counting & Visualization

```{r}

#B. Some visualisation

# Pretty much same number of observation between different types of avocado
avocado_raw %>% 
  count(type)

```

```{r}

avocado_raw %>% 
  count(region)

```

Data is actually for the 50 states


# Let's looking into doing some modelling in a univariate way

```{r}

avocado_price_albany <- avocado_raw %>% 
  filter(region=="Albany",
         type=="conventional")
```

```{r}
avocado_price_albany %>% 
  plot_time_series(.date= date,
                   .value=average_price,
                   .smooth=TRUE)
```
## CHeck on autocorrelation

```{r}

avocado_price_albany %>% 
  plot_acf_diagnostics(.date_var = date,
                       .value=average_price,
                       .show_white_noise_bars=TRUE)


```

Based on ACF plot, I would integrate value 2 to 8, 21, 61 and maybe 83

# Does the quantity sold has as well an impact, let's try to indetify this

```{r}

avocado_price_albany %>% 
  select(date:total_volume) %>% 
  plot_acf_diagnostics(.date_var = date,
                       .value=average_price,
                       .ccf_vars=total_volume,
                       .facet_ncol=2,
                       .show_white_noise_bars=TRUE)
```

Volume does have a useful cross-corellation element - lag 33 to lag 52. And and inverse correlation lag 70 to 79


# How does the seasonality come into play

```{r}
avocado_price_albany %>% 
  plot_seasonal_diagnostics(.date_var=date,
            .value=average_price,
            .feature_set=c("week","month.lbl","quarter","year"))
```
I need to get better at getting the message out from that - I can see that there seem to be some trend from each of this plot but not sure exactly how to articulate it.



# Is there any anomaly in the price?

```{r}

avocado_price_albany %>% 
  plot_anomaly_diagnostics(.date_var=date,
            .value=average_price)

```
No anomaly regarding avocado price in Albany :)


